Molecular transport in human pial perivasculature

### 2024-03-05 paper/main.tex
add small paragraph on meshing
Former-commit-id: 8fc05466de95b4ab7865a18bec0d741fea27c770

>>>>

\subsection*{Meshing}

\citet{hodneland2019new} developed a method to image the brains' microvasculature based on time-of-flight (ToF) and quantitative susceptibility mapping (QSM) to identify arterial and venous networks.
We derive a detailed tetrahedral mesh of both the parenchyma and the surrounding CSF-filled spaces alongside a network representation of the vasculature from the anatomical data provided therein.

\paragraph{3D domain}

We merge the white and grey matter masks provided by \cite{hodneland2019new} to extract the pial surface. As no data on the CSF-filled spaces is available, we smooth and extend the pial surface by about 5\,mm to obtain an approximation of the SAS and include the inner fluid-filled cavities such as the ventricular system. 
Finally, we generate a tetrahedral mesh of both compartments using the fTetWild meshing algorithm \cite{hu2020fast}.

\paragraph{Vessel networks}

We skeletonize the binary masks of both the arterial and venous network using Kiminaro \cite{william_silversmith_2021_5539913} and obtain networks consisting of centerline and radius information of all detected vessels. The resulting networks are further smoothened using a spline interpolation technique and the nodes with lowest z-coordinate are identified as the networks' root nodes.
